Model Checking Differentially Private Properties

### 2018-01-28 mdp.tex
examples
remove product mdp from figure

\begin{figure}
  \centering
  \begin{subfigure}{.40\columnwidth}
    \resizebox{\columnwidth}{!}{
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
      distance=2cm,node/.style={circle,draw}]
      \node[node] (p) at ( 0,  1.5) { $+$ };
      \node[node] (q) at ( 0, -1.5) { $-$ };
      \node[node] (F) at (-1.5,  0) { $Y$ };
      \node[node] (T) at ( 1.5,  0) { $N$ };

@@

      (F) edge [loop left] node [below] { $-, 1$ } (F)
      (T) edge [loop right] node [below] { $-, 1$ } (T)
      ;
      \end{tikzpicture}
    }
    \caption{Markov Decision Process}
    \label{figure:simple-mdp-mdp}
  \end{subfigure}
  \begin{subfigure}{.58\columnwidth}
    \resizebox{\columnwidth}{!}{
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
      distance=2cm,node/.style={circle,draw,inner sep=1pt}]
      \node[node] (pq) at (-2.1, 2.1) { $+-$ };
      \node[node] (qp) at ( 2.1,-2.1) { $-+$ };
      \node[node] (RR) at (-2.1,-2.1) { $YY$ };
      \node[node] (BB) at ( 2.1, 2.1) { $NN$ };
      \node[node] (RB) at (- .7,- .7) { $YN$ };
      \node[node] (BR) at (  .7,  .7) { $NY$ };

      \path
      (pq) edge [bend right=5] node [left=1,below=12,rotate=270] { $L, .1875$ } (RR)
      (pq) edge [bend left=5]  node [above=5,right=1] { $L, .1875$ } (BB)

      (pq) edge [bend left=5]  node [right=4,rotate=270] { $H, .16$ } (RR)
      (pq) edge [bend right=5] node [below=5,right=1] { $H, .16$ } (BB)

      (pq) edge [bend left=5]  node [left,below=10,rotate=295]  { $L, .5625$ } (RB)
      (pq) edge [bend right=5] node [left,below,rotate=330]  { $L, .0625$ } (BR)

      (pq) edge [bend right=5] node [right=2,above,rotate=300] { $H, .64$ } (RB)
      (pq) edge [bend left=5]  node [right,above,rotate=340] { $H, .04$ } (BR)

      (qp) edge [bend right=5] node [above=5,left=1] { $L, .1875$ } (RR)
      (qp) edge [bend left=5]  node [above=30,left=5,rotate=90] { $L, .1875$ } (BB)

      (qp) edge [bend left=5]  node [below=5,left=1] { $H, .16$ } (RR)
      (qp) edge [bend right=5] node [above,right=5,rotate=90] { $H, .16$ } (BB)

      (qp) edge [bend left=5]  node [left,below,rotate=330]  { $L, .0625$ } (RB)
      (qp) edge [bend right=5] node [left=3,below=3,rotate=295]  { $L, .5625$ } (BR)

      (qp) edge [bend right=5] node [left=5,above,rotate=330] { $H, .04$ } (RB)
      (qp) edge [bend left=5]  node [right=1,above=1,rotate=295] { $H, .64$ } (BR)

      (RR) edge [loop left] node [above] { $-, 1$ } (RR)
      (BB) edge [loop right] node [above] { $-, 1$ } (BB)
      (RB) edge [loop below] node [left] { $-, 1$ } (RB)
      (BR) edge [loop above] node [right] { $-, 1$ } (BR)
      ;
      \end{tikzpicture}
\hide{
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
      distance=2cm,node/.style={circle,draw,inner sep=1pt}]
      \node[node] (pq) at (   0,   0) { $+-$ };
      \node[node] (RR) at (-  2,   0) { $YY$ };
      \node[node] (BB) at (   2,   0) { $NN$ };
      \node[node] (RB) at (   0, 1.5) { $YN$ };
      \node[node] (BR) at (   0,-1.5) { $NY$ };

      \path
      (pq) edge [bend right=15] node [above] { $L, .1875$ } (RR)
      (pq) edge [bend left=15]  node [above] { $L, .1875$ } (BB)

      (pq) edge [bend left=15]  node [below] { $H, .16$ } (RR)
      (pq) edge [bend right=15] node [below] { $H, .16$ } (BB)

      (pq) edge [bend left=15]  node [left]  { $L, .5625$ } (RB)
      (pq) edge [bend right=15] node [left]  { $L, .0625$ } (BR)

      (pq) edge [bend right=15] node [right] { $H, .64$ } (RB)
      (pq) edge [bend left=15]  node [right] { $H, .04$ } (BR)

      (RR) edge [loop below] node [below] { $-, 1$ } (RR)
      (BB) edge [loop above] node [above] { $-, 1$ } (BB)
      (RB) edge [loop left] node [left] { $-, 1$ } (RB)
      (BR) edge [loop right] node [right] { $-, 1$ } (BR)
      ;
      \end{tikzpicture}
}
    }
    \caption{Product Markov Decision Process}
    \label{figure:simple-mdp-product}
  \end{subfigure}
  \caption{Markov Decision Process and its Self-Product}
  \label{figure:simple-mdp}
\end{figure}

@@

>>>>

\begin{wrapfigure}{r}{.5\columnwidth}
  \centering
    \resizebox{.4\columnwidth}{!}{
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
      distance=2cm,node/.style={circle,draw}]
      \node[node] (p) at ( 0,  1.5) { $+$ };
      \node[node] (q) at ( 0, -1.5) { $-$ };
      \node[node] (F) at (-1.5,  0) { $Y$ };
      \node[node] (T) at ( 1.5,  0) { $N$ };

@@

      (F) edge [loop left] node [below] { $-, 1$ } (F)
      (T) edge [loop right] node [below] { $-, 1$ } (T)
      ;
      \end{tikzpicture}
    }
    \caption{Markov Decision Process}
    \label{figure:simple-mdp}
\end{wrapfigure}

@@

\lz{assume that we need reactive MDPs with absorbing states}
